### 2008-05-16 trunk/Papers/dl-gre-08/discussion.tex

\begin{figure}
\begin{center}
\includegraphics[width=0.2\textwidth]{drawers.png}
\end{center}\vspace*{-3ex}
\caption{A schematic view of the filing cabinets.}\label{fig:drawers}\vspace*{-3ex}
\end{figure}

@@

When we add relations, our algorithm is able to generate 10 of the 15
human-produced relational descriptions correctly (in addition to the
98 non-relational descriptions). This is shown in more detail in
Fig.~\ref{fig:example_outputs}, which gives example outputs of the
\el\ algorithm for three different orderings. (Notice that four of the
15 descriptions occurred twice in the corpus.) Of the five
human-produced descriptions that the \el\ algorithm cannot generate,
three involve references to sets (\textit{the two blues ones in
  horizontal sequence}/\textit{the two yellow drawers}), and two
contain so much redundant information that our algorithm, which stops
once it has found a distinguishing description, cannot
reproduce it. While the
algorithm cannot reproduce those descriptions, it does generate other,
simpler descriptions for them.

@@

In order to get a more comprehensive picture of the algorithms'
efficiency, we ran them on random models with increasing numbers of
individuals.  Each model had random interpretations for ten different
propositional and four relational symbols; each individual had a 10\%
chance to be in the extension of each propositional symbol, and each
pair of individuals had a 10\% chance to be related by a relational
symbol.  The results (averaged over 10 runs for each model size) are
shown in Fig.~\ref{fig:runtimes}.  As the figure shows, the \el\
algorithm takes about 350 ms on average to generate relational REs for
all individuals in the model of size 100, i.e.\ less than 4 ms on
average for each individual.  The \alc\ algorithm is even faster, at
about 140 ms for the model of size 100.  As far as we know, these are
by far the fastest published runtimes for any relational GRE algorithm
in the literature.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{runtimes}
  \caption{Average runtimes (in ms) of the two algorithms on random
    models with different numbers of individuals.}%%of different sizes.} 
  \label{fig:runtimes}
\end{figure}

One problem that arises in our approach specifically is that both
algorithms derive some measure of efficiency from their freedom to
build formulas without having to respect any linguistic constraints.
It seems straightforward, for instance, to extend Krahmer et al.'s
\shortcite{Krahmer2003} approach such that it only considers subgraphs
that can actually be realized, because their algorithm proceeds by a
genuine search for uniquely identifying subgraphs, and will simply
take a different branch of the search if some subgraph is useless.
This would be harder in our case.  Our algorithms don't search in the
same way; if we disallow certain refinements of a partition, we have
to allow the algorithms to backtrack and thus jeopardize the
worst-case polynomial runtime.  Investigating this interplay between
efficiency and linguistic constraints is an interesting avenue for
future research.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.2\textwidth]{drawers.png}
\end{center}\vspace*{-3ex}
\caption{A schematic view of the filing cabinets.}\label{fig:drawers}\vspace*{-1.5ex}
\end{figure}

@@

When we add relations, our algorithm is able to generate 10 of the 15
human-produced relational descriptions correctly (in addition to the
98 non-relational descriptions).  Fig.~\ref{fig:example_outputs} gives
example outputs of the \el\ algorithm for three different orderings,
which together achieve this coverage.  Of the five human-produced
descriptions that the \el\ algorithm cannot generate, three involve
references to sets (\textit{the two blues ones in horizontal
sequence}/\textit{the two yellow drawers}), and two contain so much
redundant information that our algorithm, which similar to the
Incremental Algorithm allows for some redundancy but stops once it has
found a distinguishing description, cannot reproduce them. It does,
however, generate other, simpler descriptions for all of the
human-produced descriptions that cannot be reproduced exactly.

@@

In order to get a more comprehensive picture of the algorithms'
efficiency, we ran them on random models with increasing numbers of
individuals.  Each model had random interpretations for ten different
propositional and four relational symbols; each individual had a 10\%
chance to be in the extension of each propositional symbol, and each
pair of individuals had a 10\% chance to be related by a relational
symbol.  The results (averaged over 10 runs for each model size) are
shown in Fig.~\ref{fig:runtimes}.  The \el\
algorithm takes about 350 ms on average to generate relational REs for
all individuals in the model of size 100, i.e.\ less than 4 ms on
average for each individual.  The \alc\ algorithm is even faster, at
about 140 ms for the model of size 100.  As far as we know, these are
by far the fastest published runtimes for any relational GRE algorithm
in the literature.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{runtimes}\vspace*{-2ex}
  \caption{Average runtimes (in ms) of the two algorithms on random
    models with different numbers of individuals.}
  \label{fig:runtimes}\vspace*{-1.5ex}
\end{figure}

One problem that arises in our approach is that both
algorithms derive some measure of efficiency from their freedom to
build formulas without having to respect any linguistic constraints.
It seems straightforward, for instance, to extend Krahmer et al.'s
\shortcite{Krahmer2003} approach such that it only considers subgraphs
that can actually be realized, because their algorithm proceeds by a
genuine search for uniquely identifying subgraphs, and will simply
take a different branch of the search if some subgraph is useless.
This would be harder in our case.  Our algorithms don't search in the
same way; if we disallow certain refinements of a partition, we have
to allow the algorithms to backtrack and thus jeopardize the
worst-case polynomial runtime.  Investigating this interplay between
efficiency and linguistic constraints is an interesting avenue for
future research.
